\documentclass[18pt]{letter}
\usepackage{setspace}
\onehalfspacing

\begin{document}    

\large

Madeline, our relationship has brought me great joy and meaningful happiness
over the last several years.  You've given me a deep and subtle satisfaction in an important
piece of my life, and this fulfilment has slowly become a natural part of who I am.  I never doubt that this sincere
happiness together will continue, which gives me an immense sense of
comfort and ease.  I will do my best to never take this implicit happiness you provide 
me for granted.  

As we move forward in life, the key aspects of our friendship and marriage I want to promise you are
adaptability and balance.  As our lives progress, and
both exciting and demanding times arise, I want to help you find the most fulfilment in life's experience.  Whether that means supporting you or challenging
and pushing you at times, or embracing the simple day-to-day parts of life, while finding
new things for us to experience and learn about, so that your life never feels
stagnate.  But you are a bright, caring, and
talented person, so I imagine most of the happiness I provide you will ulitmately just come from making you laugh. As we inevitably change over
time, I will try to keep the appropriate balance between our
individiual pursuits and the closeness of our relationship.  This balance has came naturally though, so I am mostly just
excited to watch you become an even more amazing person.

Finally, there are some things that will remain constant.  I will always
support you and be a base in your life.  I will always look
forward to sharing conversation with you late into the night, and I will continue loving you, through our oldest age.

\end{document}
